---
title: "Homework 7"
output: html_notebook
---

| Homework 7                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Oct 18  | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 7. Refer to the corresponding materials and
ICE (with solutions) posted on ICON. Follow all of the instructions
given on prior homeworks, referring to them as necessary.

# Exercises

# #1

Load `faithful` data set by typing data("faithful"), which gives two columns of data.
First column is the eruption time in minutes and second is the wait time until next
eruption in minutes. Create a data frame called `eruptions` with columns `Time` and
`Pause`, both as double, which will contain the output from the geyser function.

Write a function called `geyser` that takes two input arguments; the first the time
of eruptions called `length` and second the wait time between eruptions called 
`wait`. The function should add values to the `eruptions` data frame that exceed the
`length` input argument and are less than the `wait` input argument. In essence, the
function selects values that describe the degree of geyser activity desired, 
according to the given input arguments. [Hint: You do not need to do any error
handling in this function.]


```{r}



```

Create a data frame called `eruptions` with columns `Time` and `Pause`, both as 
double. Call geyser function with the inputs 3 for `length` and 70 for `wait`. Be
sure to keep the geyser function output in the `eruptions` data frame. Write the
`eruptions` data frame to a file called `eruptions.csv` to save results in a text
file.


```{r}



```

# #2

Install the "babynames" package (outside of your script), load the library 
(inside your script), and look at the help command "?babynames" in the console. 
Then write a function called `peak`, which takes two inputs, `myname` and `mysex`, 
and returns the year (as an object with class numeric/integer) in which that 
name/sex combination had its peak popularity (indicated by the highest proportion). 
For example, myname = "Yvonne" with mysex = "F" peaked in 1937. Since then, the
popularity of that name/sex combination has been decreasing (in terms of the 
proportion). See: https://rpubs.com/jalapic/babynames
[Hints: Find exact name matches only. You do not need to do any error handling in 
this function.]

```{r}



```

Create a data frame called `names` with the columns `Name`, `Sex`, and `Year` all
as character. Call the `peak` function with the input below. Add a row to 
`names` for each function call, which includes the year result returned from the
`peak` function. Write the `names` data frame to a file called `names.csv` to save
the results in a text file.

"Frank", "M"
"Zachary", "M"
"Cassandra", "F"
"Taylor", "F"
"Taylor", "M"
"Molly", "F"
"Aquila", "M"
"Jazmyn", "F"
"Gable", "M"
"Kang", "M"
"Clarie", "F"
"Misri", "F"
"Robin", "M"
"Deepak", "M"
"Sierra", "F"


```{r}



```

Create a solution.R file that contains the R code from this Rmd file. Be sure
to place the library calls at the top followed by the functions. Then have 
Part 1 and Part 2, where each code block is labeled by a comment. This order
is different from the Rmd, but is the order that a well-structured R script
would be in.
