---
title: "Homework 7"
output: html_notebook
---

| Homework 7                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Oct 18  | Business Analytics Graduate Program |
| Submit via GitHub              |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 7. Refer to the corresponding materials and
ICE (with solutions) posted on ICON. Follow all of the instructions
given on prior homeworks, referring to them as necessary.

# Exercises

# #1

In the previous homework, you created code to calculate an
approximation of the number pi/4. For your reference, here is the code
from the homework solution:

    pi_over_four <- 0
    for(i in 1:100) {
        if(i %% 4 == 1) {
            pi_over_four <- pi_over_four + 1/i
        } else if(i %% 4 == 3) {
            pi_over_four <- pi_over_four - 1/i
        }
    }

In this code, the number 100 is called the "order of approximation."
Write a function, called `pi4approx`, which takes a positive integer
`n` as input (with default `n=100`) and returns the approximation of
pi/4 using `n` as the order of approximation. If the user inputs an `n`,
which is not a positive integer, then use the default value for `n`.
Some examples of the function's usage and output are included in the
file `examples.html`.

```{r}

```

# #2

Install the `babynames` package (outside of your notebook), load
the library (inside your notebook), and look at the help command
`?babynames` in the console. Then write a function called `peak`, which
takes two inputs, `myname` and `mysex`, and returns the year (as an
object with class `numeric` or `integer`, not a data frame) in which
that name/sex combination had its peak popularity (as indicated by the
highest proportion). For example, `myname = "Samuel"` with `mysex = "M"`
peaked in 1880. Since then, the popularity of that name/sex combination
has been decreasing (in terms of the proportion). Some examples of the
function's usage and output are included in the file `examples.html`.
[Hints: Find exact name matches only. You do not need to do any error
handling in this function.]

```{r}

```
