---
title: "Homework 7"
output: html_notebook
---

| Homework 7                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Oct 18  | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 7. Refer to the corresponding materials and
ICE (with solutions) posted on ICON. Follow all of the instructions
given on prior homeworks, referring to them as necessary.

# Exercises

# #1

In console type data() to see available built in data sets in R. Next load
`faithful` data set by typing data("faithful"), which gives two columns of data.
First column is the eruption time in minutes and second is the waiting time 
until next eruption in minutes. 

Then write a function called geyser that takes two arguments, the first is the time 
of eruptions called `length` and second is the wait time between eruptions called 
`wait`. The function should build a data frame that contains geyser entries that
exceed the length and are less than the wait times.

```{r}



```

Create a data frame called `eruptions` with columns `Time` and `Pause`, both as 
double, from geyser function. Call geyser function with the inputs 3 for `length` 
and 70 for `wait`. Write the `eruptions` data frame to a file called `eruptions.csv`.


```{r}



```

# #2

Install the "babynames" package (outside of your script), load the library 
(inside your script), and look at the help command "?babynames" in the console. 
Then write a function called "peak", which takes two inputs, "myname" and "mysex", 
and returns the year (as an object with class numeric/integer) in which that 
name/sex combination had its peak popularity (indicated by the highest proportion). 
For example, myname = "Yvonne" with mysex = "F" peaked in 1937. Since then, the
popularity of that name/sex combination has been decreasing (in terms of the 
proportion). See: https://rpubs.com/jalapic/babynames
[Hints: Find exact name matches only. You do not need to do any error handling in 
this function.]

```{r}



```

Create a data frame called `names` with the columns `Name`, `Sex`, and `Year` all
as character. Call the `peak` function with the following input. Add a row to 
`names` for each, including the year result returned from the `peak` function. 
Write the `names` data frame to a file called `names.csv`.

"Frank", "M"
"Zachary", "M"
"Cassandra", "F"
"Taylor", "F"
"Taylor", "M"
"Molly", "F"
"Aquila", "M"
"Jazmyn", "F"
"Gable", "M"
"Kang", "M"
"Clarie", "F"
"Misri", "F"
"Robin", "M"
"Deepak", "M"
"Sierra", "F"


```{r}



```

Create a solution.R file that contains the R code from this Rmd file. Be sure
to place the library calls at the top followed by the functions. Then have 
Part 1 and Part 2, where each code block is labeled by a comment.